\documentclass[10pt,a4paper]{extarticle}
\pagenumbering{gobble}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{datetime}
\usepackage{graphicx}
\usepackage{charter}
\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\begin{document}
\begin{center}
    \begin{minipage}{\textwidth}
        \centering
        {\LARGE\textbf{Onur Ravli}} \hspace{2pt} {\LARGE{Software Developer}}\\[10pt]
        \href{mailto:onur@onurravli.com}{onur@onurravli.com} \textbullet\
        \href{https://onurravli.com}{onurravli.com} \textbullet\
        \href{https://linkedin.com/in/onurravli}{linkedin.com/in/onurravli} \textbullet\
        \href{https://github.com/onurravli}{github.com/onurravli}
    \end{minipage}
\end{center}

\section{Summary}
Software developer with \textbf{2 years of proven experience} in delivering scalable, type-safe web and cross-platform applications. Leverages AI-powered workflows to accelerate development cycles, automate boilerplate, and enhance code maintainability. Specialized in the Node.js ecosystem with a solid track record of collaborating with remote, international teams. Adept at tackling complex technical challenges, from integrating medical imaging workflows to designing efficient backend architectures. Focused on writing maintainable, clean code that bridges robust system design with practical product needs.

\section{Experience}
\textbf{\href{https://insiderone.com}{Insider One (fka Insider)} \textit{(Istanbul, Türkiye)}} \hfill Remote (Full-time)\\
\textit{Software Developer} \hfill July 2025 -- Present
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Supported 900+ global partners (including Singapore Airlines, AirArabia, Turkish Airlines, Samsung, ING, Allianz, IKEA, and more) by delivering user-facing web application features end-to-end in an agile cycle.
    \item Conducted code reviews, ensuring high code quality and maintainability standards.
    \item Delivered real-time technical guidance in live international client sessions, translating technical issues into clear, actionable solutions for enterprise stakeholders.
\end{itemize}
\textbf{\href{https://acanio.com/}{Acanio, LLC.} \textit{(Orlando, FL)}} \hfill Remote (Contactor)\\
\textit{Full-stack Engineer} \hfill February 2025 -- May 2025
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Developed multiple applications for medical imaging using React, React Native, and Electron, enabling cross-platform DICOM \& DCM image viewing and processing.
    \item Optimized DICOM/DCM image processing and rendering performance across web, mobile, and desktop platforms, contributing to a unified codebase shared between codebases.
\end{itemize}
\textbf{\href{https://www.dotdoc.com.tr/}{Doc Design and Informatics Co. Ltd.} \textit{(Istanbul, Türkiye)}} \hfill Remote (Full-time)\\
\textit{Full-stack Engineer} \hfill March 2024 -- October 2024
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Built applications using Node.js, Strapi.js, React Native and Electron, focusing on innovative media and educational publishing platforms.
\end{itemize}
\textbf{\href{https://jotform.com}{JotForm} \textit{(Ankara, Türkiye)}} \hfill Remote (Internship)\\
\textit{Summer Intern} \hfill August 2023 -- September 2023
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Developed a revision history system for Jotform Approvals using Node.js, React, PHP, and MySQL in a collaborative team environment.
\end{itemize}
\textbf{\href{https://www.ustunova.com.tr}{Üstünova Engineering} \textit{(Ankara, Türkiye)}} \hfill Ankara, Türkiye (Internship)\\
\textit{Summer Intern} \hfill July 2023 -- August 2023
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Built dashboard and control panel interfaces for EV charging station software (Electr-INN).
\end{itemize}

\section{Skills}
\textbf{Programming Languages:} TypeScript, JavaScript, Python \\
\textbf{Backend Tools:} Express.js, Nest.js, GraphQL, Supabase \\
\textbf{Frontend Tools:} React.js, Next.js, Tailwind CSS, React Native, Expo, Electron \& Tauri \\
\textbf{Databases:} PostgreSQL, MongoDB, MySQL, Redis \\
\textbf{Cloud \& DevOps:} Docker, Docker Compose, Core AWS Services, Terraform \& Terragrunt \\
\textbf{Other Tools:} Jest, Postman, Swagger, Git, Claude Code, Cursor, Vercel SDK
\section{Projects}
\textbf{\href{https://github.com/libresuite/libresuite}{LibreSuite}} An open-source, scalable, event-driven collaboration suite. \textit{(Express.js, Next.js, Kafka, Docker)}\\
\textbf{\href{https://github.com/onurravli/locallm}{LocaLLM}} Local first LLM-based development suite. \textit{(Next.js, LM Studio)}\\
\textbf{\href{https://getmapino.com}{Mapino}} Map based social mobile application. \textit{(Swift, Supabase, Express.js)}\\
\textbf{\href{https://github.com/bowie-lang/bowie}{Bowie Language}} Dynamically typed, interpreted scripting language written in C. \textit{(C, Make)}\\
\textbf{\href{https://github.com/onurravli/flottant}{Flottant}} A browser-based DAW (Digital Audio Workstation). \textit{(Next.js, Web Audio API)}

\section{Education}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item 
    \textbf{Konya Technical University} \hfill Konya, Türkiye\\
    \textit{B.Sc. in Computer Engineering} \hfill September 2022 -- Present
    \item
    \textbf{Konya Technical University} \hfill Konya, Türkiye\\
    \textit{B.Sc. in Electrical \& Electronics Engineering} \hfill September 2020 -- June 2022 (Undergraduate Transfer)
\end{itemize}
\end{document}
